We want teachers to be more aware of the award, so that they may start to eventually care about receiving the award. We want the award to be something that the teacher can look forward to. The most obvious approach is to make announcements at staff meetings. I propose two announcements:
\begin{enumerate}
\item The first announcement can be at the start of the year. This can be used to announce the new categories for the year, and to get the teacher's feedback on these categories.
\item The second announcement can be at the meeting before voting opens, to ask if they could advertise the voting procedure during their last lecture. This serves to attract more voters, but also to act as a reminder to the teachers.
\end{enumerate}

Furthermore, we want students to be more aware of the award as well. The more students that vote (and talk about the vote) the more legitimacy the award acquires. While we do not have any concrete ideas on how to improve the current system (which is simply a post on Nestor), we have thought of the following options:
\begin{itemize}
\item A post on the Nice-To-Know tab, on Nestor.
\item Physical fliers to be distributed in the study landscape.
\item A poster, in the study landscape / on the COVER board.
\item A raffle for the voters to win something. For example:
    \begin{itemize}
        \item A chance to add questions to the winner interview (see \ref{interview})
        \item A chance to add a new category for next years award
        \item A box of chocolates
    \end{itemize}
\item We can host a website for the whole contest. There are many benefits here:
    \begin{itemize}
        \item It's more substantial than a Nestor announcement. It makes the contest seem like the organizers are more invested in its success.
        \item We can make voting much smoother, since the process is infinitely more customizeable. We can provide each student a one-time-token tied to their student number for election integrity.
        \item There's a sense of permanence to the award. A simple Nestor announcement seems ethereal, whereas we can have a showcase for past winners.
    \end{itemize}
    
    Obviously this item is a lot more work but I (Channa) would be happy to code it up.
\end{itemize}